publications

### 2023-02-15 papers.Rmd
updated cv and pubs

**Parsons, S** (2020). Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability. *accepted for publication at Meta-Psychology*. Preprint: [psyarxiv.com/y6tcz](https:/psyarxiv.com/y6tcz), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)   [<i class="fas fa-download"></i> PDF](papers/20_Parsons_2022_MetaPsychology_acceptedpreprint.pdf)

@@

>>>>

**Parsons, S** (2022). Exploring reliability heterogeneity with multiverse analyses: Data processing decisions unpredictably influence measurement reliability. *accepted for publication at Meta-Psychology*. DOI: [doi.org/10.15626/MP.2020.2577](https://doi.org/10.15626/MP.2020.2577), data and code: [osf.io/haz6u/](https://osf.io/haz6u/)   [<i class="fas fa-download"></i> PDF](papers/20_Parsons_2022_MetaPsychology_acceptedpreprint.pdf)

@@

**Parsons, S.**, Brandmaier, A., Lindenberger, U., & Kievit. (2023). Longitudinal stability of grey matter measures varies across brain regions, imaging metrics, and testing sites in the ABCD study. Preprint: https://psyarxiv.com/zpu6t/

Zavlis, O., **Parsons, S.**, Fox, E., Booth, C., Songco, S., & Vincent, J. (December, 2022). The effects of life experiences and polygenic risk for depression on the development of positive and negative cognitive biases across adolescence: The CogBIAS hypothesis. Preprint: https://psyarxiv.com/wsn4x/

**Parsons, S.** & McCormick, E. M. (November, 2022). “Don’t peek at your data” applies to longitudinal studies too: two time points poorly capture trajectories of change. Preprint: https://psyarxiv.com/

Todorovic, A., *Parsons, S.*, Chapple, L., Taylor, A., & Fox, E. (2022, April 29). Lower, not higher, trait anxiety leads to switch cost asymmetry on neutral tasks: a replication and extension of Gustavson et al., 2017. https://doi.org/10.31234/osf.io/aer8b
